An experimental, extensible units package for R
===============================================

Most physical quantities carry units. This package defines a new class, `Quantity`, which allows numerical quantities in R to carry their physical units. Simple operations (`+`, `-`, `*`, `/`, and `^`) on quantities deal correctly with their units (and complain when the operation is not allowed by dimensional analysis). Conversion of units is supported. 

Presently undocument and little commented.
```{r, echo = FALSE, include = FALSE}
library(devtools)
load_all(reset = TRUE)
```

Examples
--------

### Defining simple quantities
```{r}
m1 <- as.Quantity(1, "kg")
m2 <- as.Quantity(2, "kg")
```
### Arithmetic with quantities
```{r}
2 * m1
m1 + m2
```
Quantities must have compatible units to be added.
```{r}
l1 <- as.Quantity(2.54, "cm")
m1 + l1
```

### Conversion of units
The full set of SI prefixes is supported.
```{r}
as.Quantity(m1, "µg")
```
Names are available in case you forget.
```{r}
name.unit("YJ")
```
Complex units are expressed in the usual notation. Multiplication is indicated with a space, powers by `^`. (The solidus (`/`) is not yet supported.) Parentheses group subnits. 
```{r}
e1 <- as.Quantity(10, "GW h")
as.Quantity(e1, "ktoe")
```
The dimension of a derived dimension is given by writing it in square brackets. 
```{r}
e2 <- as.Quantity(10, "(GW h)_[energy]")
```
The system distinguishes between the dimensions of `e1`, which are `power x time`, and the dimension of `e2`, which is `energy`. 

### Extensibility
Units can be added to the list of known units.
```{r}
## The unit "tonnes of coal equivalent" is not defined in the siunits package.
e2  <- as.Quantity(1, "tce")
```
The definition of tce is 7 gigacalories, and the calorie is already part of the siunits package. The argument `gen.prefixes = TRUE` causes the full set of SI-prefixed units to be added.
```{r}
add_unit("energy", "tce", "tonne of coal equivalent", "tonnes of coal equivalent", multiple = as.Quantity(7, "Gcal"), gen.prefixes = TRUE)
as.Quantity(1, "tce")
``` 
Not only `tce` but the full set of prefixed units will have been created.
```{r}
name.unit("Mtce")
```

### More complex constructions
Emissions factors have dimensions of mass per unit energy.
```{r}
gas.CO2 <- as.Quantity(0.185, "kg (kW h)^-1") # These are the units in DUKES
```
Conversions are straightforward:
```{r}
as.Quantity(gas.CO2, "kg therm^-1")
```
Emissions are the product of an emissions factor and an energy. The energy does not have to be in the same units as that in which the emissions are expressed.
```{r}
CO2 <- gas.CO2 * as.Quantity(1, "ktoe")
CO2
```
The result keeps all the dimensions and units in the factors. Nonetheless, the result is a mass, so can be converted to any convenient unit with dimension `mass`.
```{r}
as.Quantity(CO2, "kt")
```

