An experimental, extensible units package for R
===============================================

Most physical quantities carry units. This package defines a new class, "quantity"", which allows numerical quantities in R to carry their phsyical units. Simple operations ("+", "-", "*", "/", "^") on quantities deal correctly with their units (and complain when the operation is not allowed by dimensional analysis). Conversion of units are supported. 

Presently undocument and little commented.

```{r, echo = FALSE, include = FALSE}
library(devtools)
load_all(reset = TRUE)
```

Examples
--------

### Defining simple quantities
```{r}
m1 <- as.Quantity(1, "kg")
m2 <- as.Quantity(2, "kg")
2 * m1
m1 + m2
```

### Conversion of units
```{r}
as.Quantity(m1, "g")
e1 <- as.Quantity(10, "GW h")
as.Quantity(e1, "ktoe")
```

### Extensibility
```{r}
## The unit "tonnes of coal equivalent" is not defined.
as.Quantity(e1, "tce")

add_unit("energy", "tce", "tonne of coal equivalent", "tonnes of coal equivalent", multiple = as.Quantity(7, "Gcal"), gen.prefixes = TRUE)
as.Quantity(e1, "tce")
```

### More complex constructions
```{r}
gas.CO2 <- as.Quantity(0.185, "kg (kW h)_[energy]^-1")
as.Quantity(gas.CO2, "kg therm^-1")
gas <- as.Quantity(1, "ktoe")
gas * gas.CO2
as.Quantity(gas * gas.CO2, "kt")
```

